% Sneha, Guy, Nathan
First of all, I want to thank my supervisor, Sneha Malde, for four years of invaluable, always-honest guidance, and for teaching me the ropes of being an experimental particle physicist.
% and for being an inspiration in setting ambitious goals in physics, life, and the combination thereof and her determination in achieving them. 
I could not have asked for a better, more involved supervisor and colleague, and I am very proud of the work that we have done together.
%
I would also like to thank Guy Wilkinson for his supervision while Sneha was on maternity leave. 
%
Finally, I want to thank  Nathan Jurik for his countless pieces of advice, insights, and ideas while cooperating on my first analysis, and for at least as many celebratory pints afterwards.

% Monies
I am grateful to the many organisations that have funded my research degree: first and foremost the Royal Society for providing my main funding, and to Aage \& Johanne Louis-Hansens Fond, St. Anne's College, Knud H\o jgaards Fond, Augustinusfonden, Hery Shaws Legat, and the Anglo-Danish Society for generous additional scholarships that made my stays in Oxford and Geneva possible.

% LHCb group, Santiago, Jesse, others, St Anne's
My time in Oxford would certainly not have been the same without the many friends I've made here. I feel lucky to have shared the LHCb offices in Oxford and at CERN with an ever-changing, always-friendly bunch of fellow students (including at least one ATLAS infiltrator), with whom I've shared many enjoyable breaks, Monday push-ups, diplomatic schemes, plug-related memes, \texttt{ROOT}-induced frustrations, and warm English ales. The same can be said for the wider group of Particle Physics students, and especially Santiago, the most trusty table-football and beer-brewing buddy anyone could wish for. 
%
Likewise, the St. Anne's College MCR and boat club have brought me many good memories, of formal dinners and second desserts, of icy sunrises on the Isis, and of the sweet iron taste of a well-earned bump. 
%
Last but not least, as an expat, it has been an absolute pleasure to keep my Danish fluent by showing the University to visitors from home, trying to teach my house mates the word \emph{br\o d} for 1.5 years, and sharing a \emph{jule\o l} or two with other Danes in Oxford.

% Family and Anne Liv
Finally, I'm grateful to my family for their life-long love and for their trust that I can manage not to do too many stupid things; and I am eternally in debt to Anne Liv for her patience when I do just that, for her love and support during the last few years, and for the many adventures yet to come.